\LARGE The Bitcoin Lightning Network:\\ \Large Scalable Off-Chain Instant Payments

### 2015-11-04 paper.tex
Many corrections to the Lightning whitepaper
- Many random fixes (typos, unclear ideas, incorrect acronyms, etc.).
- A Makefile for building the PDF.

The bitcoin protocol can encompass the global financial transaction volume in
all electronic payment systems today, without a single custodial third party
holding funds or requiring participants to have any more than a computer on a
home broadband connection. A decentralized system is proposed whereby
transactions are sent over a network of micropayment channels (a.k.a. payment
channels or transaction channels) whose transfer of value occurs
off-blockchain. If Bitcoin transactions can be signed with a new sighash type
that addresses malleability, these transfers may occur between untrusted
parties along the transfer route by contracts which, in the event of
uncooperative or hostile participants, are enforceable via broadcast over the
bitcoin blockchain in the event of uncooperative or hostile participants,
through a series of decrementing timelocks.

@@

The Bitcoin\cite{nakamoto} blockchain holds great promise for distributed
ledgers, but the blockchain as a payment platform, by itself, cannot cover the
world's commerce anytime in the near future. The blockchain is a gossip
protocol whereby all state modifications to the ledger are broadcast to all
participants. It is through this ``gossip protocol'' that consensus of the
state, everyone's balances, is agreed upon. If each node in the bitcoin network
must know about every single transaction that occurs globally, that may create
a significant drag on the ability for the network to encompass all global
financial transactions. It would instead be desirable to encompass all
transactions in a way that doesn't sacrifice the decentralization and security
that the network provides.

The payment network Visa has achieved 47,000 peak transactions per second on its
network during the 2013 holidays\cite{visa}, and averages hundreds of millions
per day. Currently, Bitcoin supports less than 7 transactions per second with a
1 megabyte block limit. If we use an average of 300 bytes per bitcoin
transaction and assumed unlimited block sizes, an equivalent capacity to peak
Visa transaction volume of 47,000/tps would be nearly 8 gigabytes per Bitcoin
block, every ten minutes on average. Continuously, that would be over 400
terabytes per year. Clearly, that isn't feasible today. No home computer in the
world can operate with that kind of bandwidth and storage. If Bitcoin is to
replace all electronic payments in the future, not just Visa, it would result in
outright collapse of the Bitcoin network, or at best, extreme centralization of
Bitcoin nodes and miners to the only ones who could afford it. This
centralization would then defeat aspects of network decentralization that make
Bitcoin secure, as the ability for entities to validate the chain is what
allows Bitcoin to ensure ledger accuracy and security. Having fewer validators
due to larger blocks not only implies fewer individuals ensuring ledger
accuracy, but also results in fewer entities that would be able to validate the
blockchain as part of the mining process, which results in encouraging miner
centralization. Extremely large blocks, for example in the above case of 8
gigabytes every 10 minutes on average, would imply that only a few parties
would be able to do block validation. This creates a great possibility that
entities will end up trusting centralized parties. Having privileged trusted
parties creates a social trap whereby the central party will not act in the
interest of an individual (principal-agent problem), e.g. rentierism by
charging higher fees to mitigate the incentive to act dishonestly. In extreme
cases, this manifests as individuals sending funds to centralized trusted
custodians who have full custody of customers funds. Such arrangements, as are
common today, create severe counterparty risk. A prerequisite to prevent that
kind of centralization from occurring would require the ability for bitcoin to
be validated by a single consumer-level computer on a home broadband
connection. By ensuring that full validation can occur cheaply, Bitcoin nodes
and miners will be able to prevent extreme centralization and trust, which
ensures extremely low transaction fees.

@@

To achieve much higher than 47,000 transactions per second using Bitcoin
requires conducting transactions off the Bitcoin blockchain itself. It would be
even better if the bitcoin network supported a near-unlimited number of
transactions per second with extremely low fees for micropayments. Many
micropayments can be sent sequentially between two parties to enable any size
of payments. Micropayments would enable unbunding, less trust and
commodification of services, such as payments of per-megabyte of internet
service. To be able to achieve these micropayment use cases, however, would
require severely reducing the amount of transactions that end up being
broadcast on the global Bitcoin blockchain.

@@

If the balance in the channel were 0.05 for Alice and 0.05 to Bob, and the
transaction is now 0.07 to Alice and 0.03, the network needs to know which one
is the current balance. Blockchain transactions solve this problem by using the
blockchain ledger as a timestamping system. At the same time, it is desirable
to create a system which does not actively use this timestamping system unless
absolutely necessary, as it can become costly to the network.

@@

By chaining together multiple micropayment channels, it is possible to create a
network of transaction paths. Paths can be routing using a BGP-like system, and
the sender may designate a particular path to the recipient. The output scripts
are encumbered by a hash, which is generated by the recipient. By disclosing
the input to that hash, the recipient's counterparty will be able to pull funds
along the route.

@@

Since the Funding Transaction has already entered into the blockchain, and the
output are a 2-of-2 multisignature transaction which requires the agreement of
both parties to spend from, Commitment Transactions are used to express the
present balance. If only one 2-of-2 signed Commitment Transaction is exchanged
between both parties, then both parties will be sure that they are able to get
their money back after the Funding Transaction enters the blockchain. Both
parties do not broadcast the Commitment Transactions onto the blockchain until
they want to close out the current balance in the channel. They do so by
broadcasting the present Commitment Transaction.

@@

Since any signed Commitment Transaction may be broadcast on the blockchain, and
only one can be successfully broadcast, it is necessary to enforce that old
Commitment Transactions do not get broadcast. It is not possible to revoke tens
of thousands of transactions in Bitcoin, so an alternate method is necessary.
Instead of active revocation enforced by the blockchain, it's necessary to
construct the channel itself in similar manner to a Fidelity Bond, whereby both
parties make commitments, and violations of these commitments are enforced by
penalties. If one party violates their agreement, then they will lose all the
money in the channel.

@@

Mark Freidenbach has proposed that Sequence Numbers can be enforcible via a
relative block maturity of the parent transaction via a
soft-fork\cite{seqnum}. This would allow some basic ability to ensure some form
of relative block confirmation time lock on the spending script. In addition, an
additional opcode, OP\_CHECKSEQUENCEVERIFY (a.k.a.
OP\_RELATIVECHECKLOCKTIMEVERIFY), would permit further abilities,
including allowing a stop-gap solution before a more permanent solution for
resolving transaction malleability. A future version of this paper will include
proposed solutions.

@@

However, this requires some kind of flag in the block to designate whether it
is a timestop block. For full SPV compatibility (Simple Payment Verification;
lightweight clients), it is desirable for this to be within the 80-byte block
header instead of in the coinbase. There are two places which may be a good
place to put in this flag in the block header: in the block time and in the
block version. The block time may not be safe due to the last bits being used as
an entropy source for some ASIC miners, therefore a bit may need to be consumed
for timestop flags. Another option would be to hardcode timestop activation as a
hard consensus rules (e.g. via block size), however this may make things less
flexible. By setting sane defaults for timestop rules, these rules can be
changed without consensus soft-forks.

@@

The intent of creating a new Commitment Transaction is to invalidate all old
Commitment Transactions when updating the new balance with a new Commitment
Transaction. Invalidation of old transactions can happen by making an output be
a Revocable Sequence Verification Contract (RSMC). To invalidate a transaction,
a superseding transaction will be signed and exchanged by both parties that 
gives all funds to the counterparty in the event an older transaction is
incorrectly broadcast. The incorrect broadcast is identified by creating two
different Commitment Transactions with the same final balance outputs, however
the payment to oneself is encumbered by a RSMC.

In effect, there are two Commitment Transactions from a single Funding
Transaction 2-of-2 outputs. Of these two Commitment Transactions, only one can
enter into the blockchain. Each party within a channel has one version of this
contract. So if this is the first Commitment Transaction pair, Alice's
Commitment Transaction is defined a C1a, and Bob's Commitment Transaction is
defined as C1b. By broadcasting a Commitment Transaction, one is requesting for
the channel to close out and end. The first two outputs for the Commitment
Transaction include a Delivery Transaction (payout) of the present unallocated
balance to the channel counterparties. If Alice broadcasts C1a, one of the
output is spendable by D1a, which sends funds to Bob. For Bob, C1b is spendable
by D1b, which sends funds to Alice. The Delivery Transaction (D1a/D1b) is
immediately redeemable and is not encumbered in any way in the event the
Commitment Transaction is broadcast.

@@

After the Commitment Transaction has been in the blockchain for 1000 blocks,
Bob can then broadcast the Revocable Delivery transaction. He must wait 1000
blocks to prove he has not revoked this Commitment Transaction (C1b). After
1000 blocks, the Revocable Delivery transaction will be able to be included in a
block. If it is attempted to be included in a block before 1000 confirmations,
the transaction will be invalid up until after 1000 confirmations have passed
(at which point it will become valid if the output has not yet been redeemed).

@@

\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1.3\linewidth]{figures/newcommit-br.pdf}
	}
	\caption{
		When C2a and C2b exists, both exchange Breach Remedy
		transactions. Both parties now have explicit economic incentive
		to avoid broadcasting old Commitment Transactions (C1a/C1b).
		If either party wishes to close out the channel, they will only
		use C2a (Alice) or C2b (Bob). If Alice broadcasts C1a, all her
		money will go to Bob. If Bob broadcasts C1b, all her money will
		go to Alice. See previous figure for C2a/C2b outputs.
	}
\end{figure}

@@

To create revocable Commitment Transactions, it requires proper construction of
the channel from the beginning, and only signing transactions which may be
broadcast at any time in the future, while ensuring that one will not lose out
by uncooperative or malicious counterparties. This requires determining which
public key to use for new commitments, as using SIGHASH\_NOINPUT requires using
unique keys for each Commitment Transaction RSMC (and HTLC) output. We use $P$
to designate pubkeys and $K$ to designate the corresponding private key used to
sign.

When generating the first Commitment Transaction, Alice and Bob agree to create
a multisig output from a Funding Transaction with a single $multisig(P_{AliceF},
P_{BobF})$ output, funded from 0.5 from Alice and Bob for a total of 1 BTC. This
output is a Pay to Script Hash\cite{p2sh} transaction, which requires both Alice
and Bob to both agree to spend from the Funding Transaction. They do not yet
make the Funding Transaction (F) spendable. Additionally, $P_{AliceF}$ and
$P_{BobF}$ are only used for the Funding Transaction, they are not used for
anything else.

Since the Delivery transaction is just a P2PKH output (bitcoin addresses
beginning with 1) or P2SH transaction (commonly recognized as addresses
beginning with the 3) which the counterparties designates
beforehand, this can be generated as an output of $P_{AliceD}$ and $P_{BobD}$.
For simplicity, these output addresses will remain the same throughout the
channel, since its funds are fully controlled by its designated recipient after
the Commitment Transaction enters the blockchain. If desired, but not
necessary, both parties may update and change $P_{AliceD}$ and $P_{BobD}$ for
future Commitment Transactions.

@@

The purpose of an HTLC is to allow for global state across multiple nodes via
hashes. This global state is ensured by time commitments and time-based
unencumbering of resources via disclosure of preimages. Transactional "locking"
occurs globally via commitments, at any point in time a single participant is
responsible for disclosing to the next participant whether they have knowledge
of the preimage $R$. This construction does not require custodial trust in one's
channel counterparty, nor any other participant in the network.

@@

\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1\linewidth]{figures/htlc-concept.pdf}
	}
	\caption{This is a non-functional naive implementation of an HTLC. Only
		the HTLC path from the Commitment Transaction is displayed. Note
		that there are two possible spends from an HTLC output. If Bob
		can produce the preimage $R$ within 3 days and he can redeem
		path 1. After three days, Alice is able to broadcast path 2.
		When 3 days have elapsed either is valid. This model, however
		doesn't work with multiple Commitment Transactions.
	}
\end{figure}

@@

After HT1a enters into the blockchain and 1000 block confirmations, a HTLC
Timeout Revocable Delivery transaction (HTRD1a) may be broadcast by Alice which
consumes $multisig(P_{Alice3}, P_{Bob3})$. Only Alice can broadcast HTRD1a 1000
blocks after HT1a is broadcast since only Bob gave his signature for HTRD1a to
Alice. This transaction can be revocable when another transaction supersedes
HTRD1a using $multisig(P_{Alice4}, P_{Bob4})$ which does not have any block
maturity requirements.

@@

After HE1b enters into the blockchain and 1000 block confirmations, a HTLC
Execution Revocable Delivery transaction (HERD1b) may be broadcast by Bob which
consumes $multisig(P_{Alice7}, P_{Bob7})$. Only Bob can broadcast HERD1b 1000
blocks after HE1b is broadcast since only Alice gave her signature for HERD1b to
Bob. This transaction can be revocable when another transaction supersedes
HERD1b using $multisig(P_{Alice8}, P_{Bob8})$ which does not have any block
maturity requirements.

@@

For example, Alice wishes to terminate the HTLC, Alice will disclose
$K_{Alice1}$ and $K_{Alice4}$ to Bob. Correspondingly if Bob wishes to terminate
the HTLC, Bob will disclose $K_{Bob1}$ and $K_{Bob4}$ to Alice. After the
private keys are disclosed to the counterparty, if Alice broadcasts C2a, Bob
will be able to take all the funds from the HTLC immediately. If Bob broadcasts
C2b, Alice will be able to take all funds from the HTLC immediately. Note that
when an HTLC is terminated, the older Commitment Transaction must be revoked as
well.

@@

Since both parties are able to prove to each other about the current state to
each other, they can come to agreement on the current balance inside the
channel. Since they may broadcast the current state on the blockchain, they are
able to come to agreement on netting out and terminating the HTLC with a new
Commitment Transaction.

@@

\begin{enumerate}
	\item Alice signs and sends her signature for RD3b and C3b. At this
		point Bob can elect to broadcast C3b or C2b (with the HTLC) with
		the same payout. Bob is willing after receiving C3b to close out
		C2b.
	\item Bob signs and sends his signature for RD3a and C3a, as well as his
		private keys used for Commitment 2 and the HTLC being
		terminated; he sends Alice $K_{BobRSMC2}$, $K_{Bob5}$, and
		$K_{Bob8}$. At this point Bob should only broadcast C3b and
		should not broadcast C2b as he will lose all his money if he
		does so. Bob has fully revoked C2b and the HTLC. Alice is
		willing after receiving C3a to close out C2b.
	\item Alice signs and sends her signature for RD3b and C3b, as well as
		her private keys used for Commitment 2 and the HTLC being
		terminated; she sends Bob $K_{AliceRSMC2}$, $K_{Bob1}$, and
		$K_{Bob4}$. At this point neither party should broadcast
		Commitment 2, if they do so, their funds will be going to the
		counterparty. The old Commitment and old HTLC are now revoked
		and fully terminated. Only the new Commitment 3 remains, which
		does not have at HTLC.
\end{enumerate}

@@

It is possible for each participant to generate different versions of
transactions to ascribe blame as to who broadcast the transaction on the
blockchain. By having the knowledge who broadcast a transaction and the ability
to ascribe blame, a third party service can be used to hold fees in a 2-of-3
multisig escrow. If one wishes to broadcast the transaction chain instead of
agreeing to do a Funding Close or replacement with a new Commitment Transaction,
one would communicate with the third party and broadcast it to the blockchain.
If the counterparty refuses the notice from the third party to cooperate, the
penalty is rewarded to the non-cooperative party. In most instances,
participants may be indifferent to the transaction fees in the event of an
uncooperative counterparty.

@@

It is possible construct a cryptographically provable ``Delivery Versus
Payment'' contract, or pay-to-contract\cite{paytocontract}, as proof of
payment. This proof can be established as knowledge of the input R from hash(R)
as payment of a certain value. By embedding the contract between the buyer and
seller that knowing R is proof of funds sent, the recipient of funds has no
incentive to disclose R unless they have certainty that they will receive
payment. When the funds eventually get pulled from the buyer by their
counterparty in their micropayment channel, R is disclosed as part of that pull
of funds. One can design paper legal documents that specify that knowledge or
disclosure of R implies fulfillment of payment. The sender can arrange a
cryptographically signed contract for knowledge of inputs for hashes as
fulfillment of contracts before payment.

@@

The obligation to deliver funds to an end-recipient is achieved through a
process of chained delegation. Each participant along the path assumes the
obligation to deliver to a particular recipient. They pass on this obligation
to the next participant in the path. The obligation of each subsequent
participant along the path, defined in their respective HTLCs, has a shorter
time to completion compared to the prior participant. This way each participant
is sure that they will be able to claim funds when the obligation is sent along
the path.

@@

Decrementing timelocks are used so that all parties along the path know that
the disclosure of R will be able to pull funds, since they will at worst be
pulling funds after the date whereby they must receive R. If Dave does not
produce R within 1 day to Carol, then Carol will be able to close out the HTLC.
If Dave broadcasts R after 1 day, then he will not be able to pull funds from
Carol. Carol's responsibility to Bob occurs on day 2, so Carol will never be
responsible for payment to Dave without an ability to pull funds from Bob
provided that she updates her transaction with Dave to the blockchain or via
novation.

In the event that R gets disclosed to the participants halfway through expiry
along the path (e.g. day 2), then it is possible for some parties along the
path to be enriched. The sender will be able to know R, so due to Pay to
Contract, the payment will have been fulfilled even though the receiver did not
receive the funds. Therefore, the receiver will never disclose R unless they
have received an HTLC from their channel counterparty; they are guaranteed to
receive payment from one of their channel counterparties upon disclosure of the
preimage.

@@

It is necessary to use a small payment per HTLC. One should not use an extremely
high payment, in case the payment does not fully route to its destination. If
the payment does not reach its destination and one of the participants along the
path is uncooperative, it is possible that the sender must wait until the expiry
before receiving a refund. Delivery may be lossy, similar to packets on the
internet, but the network cannot outright steal funds in transit. Since
transactions don't hit the blockchain with cooperative channel counterparties,
it is recommended to use as small of a payment as possible. A tradeoff exists
between locking up transaction fees on each hop versus the desire to use as
small transaction amounts as possible (which the latter may incur higher total
fees). Smaller transfers with more intermediaries imply a higher percentage paid
as Lightning Network fees to the intermediaries.

@@

%bibliography
\bibliographystyle{unsrt}
\bibliography{new}

>>>>

The bitcoin protocol can encompass the global financial transaction volume in
all electronic payment systems today, without a single custodial third party
holding funds or requiring participants to have anything more than a computer
using a broadband connection. A decentralized system is proposed whereby
transactions are sent over a network of micropayment channels (a.k.a. payment
channels or transaction channels) whose transfer of value occurs
off-blockchain. If Bitcoin transactions can be signed with a new sighash type
that addresses malleability, these transfers may occur between untrusted
parties along the transfer route by contracts which, in the event of
uncooperative or hostile participants, are enforceable via broadcast over the
bitcoin blockchain in the event of uncooperative or hostile participants,
through a series of decrementing timelocks.

@@

The Bitcoin\cite{nakamoto} blockchain holds great promise for distributed
ledgers, but the blockchain as a payment platform, by itself, cannot cover the
world's commerce anytime in the near future. The blockchain is a gossip
protocol whereby all state modifications to the ledger are broadcast to all
participants. It is through this ``gossip protocol'' that consensus of the
state, everyone's balances, is agreed upon. If each node in the bitcoin network
must know about every single transaction that occurs globally, that may create
a significant drag on the ability of the network to encompass all global
financial transactions. It would instead be desirable to encompass all
transactions in a way that doesn't sacrifice the decentralization and security
that the network provides.

The payment network Visa achieved 47,000 peak transactions per second (tps) on
its network during the 2013 holidays\cite{visa}, and currently averages hundreds
of millions per day. Currently, Bitcoin supports less than 7 transactions per
second with a 1 megabyte block limit. If we use an average of 300 bytes per
bitcoin transaction and assumed unlimited block sizes, an equivalent capacity to
peak Visa transaction volume of 47,000/tps would be nearly 8 gigabytes per
Bitcoin block, every ten minutes on average. Continuously, that would be over
400 terabytes of data per year.

Clearly, achieving Visa-like capacity on the Bitcoin network isn't feasible
today. No home computer in the world can operate with that kind of bandwidth and
storage. If Bitcoin is to replace all electronic payments in the future, and not
just Visa, it would result in outright collapse of the Bitcoin network, or at
best, extreme centralization of Bitcoin nodes and miners to the only ones who
could afford it. This centralization would then defeat aspects of network
decentralization that make Bitcoin secure, as the ability for entities to
validate the chain is what allows Bitcoin to ensure ledger accuracy and
security.

Having fewer validators due to larger blocks not only implies fewer individuals
ensuring ledger accuracy, but also results in fewer entities that would be able
to validate the blockchain as part of the mining process, which results in
encouraging miner centralization. Extremely large blocks, for example in the
above case of 8 gigabytes every 10 minutes on average, would imply that only a
few parties would be able to do block validation. This creates a great
possibility that entities will end up trusting centralized parties. Having
privileged, trusted parties creates a social trap whereby the central party will
not act in the interest of an individual (principal-agent problem), e.g.
rentierism by charging higher fees to mitigate the incentive to act dishonestly.
In extreme cases, this manifests as individuals sending funds to centralized
trusted custodians who have full custody of customers' funds. Such arrangements,
as are common today, create severe counterparty risk. A prerequisite to prevent
that kind of centralization from occurring would require the ability for bitcoin
to be validated by a single consumer-level computer on a home broadband
connection. By ensuring that full validation can occur cheaply, Bitcoin nodes
and miners will be able to prevent extreme centralization and trust, which
ensures extremely low transaction fees.

@@

To achieve much higher than 47,000 transactions per second using Bitcoin
requires conducting transactions off the Bitcoin blockchain itself. It would be
even better if the bitcoin network supported a near-unlimited number of
transactions per second with extremely low fees for micropayments. Many
micropayments can be sent sequentially between two parties to enable any size
of payments. Micropayments would enable unbunding, less trust and
commodification of services, such as payments for per-megabyte internet
service. To be able to achieve these micropayment use cases, however, would
require severely reducing the amount of transactions that end up being
broadcast on the global Bitcoin blockchain.

@@

If the balance in the channel is 0.05 BTC to Alice and 0.05 BTC to Bob, and the
balance after a transaction is 0.07 BTC to Alice and 0.03 BTC to Bob, the
network needs to know which set of balances is correct. Blockchain transactions
solve this problem by using the blockchain ledger as a timestamping system. At
the same time, it is desirable to create a system which does not actively use
this timestamping system unless absolutely necessary, as it can become costly to
the network.

@@

By chaining together multiple micropayment channels, it is possible to create a
network of transaction paths. Paths can be routed using a BGP-like system, and
the sender may designate a particular path to the recipient. The output scripts
are encumbered by a hash, which is generated by the recipient. By disclosing
the input to that hash, the recipient's counterparty will be able to pull funds
along the route.

@@

Since the Funding Transaction has already entered into the blockchain, and the
output is a 2-of-2 multisignature transaction which requires the agreement of
both parties to spend from, Commitment Transactions are used to express the
present balance. If only one 2-of-2 signed Commitment Transaction is exchanged
between both parties, then both parties will be sure that they are able to get
their money back after the Funding Transaction enters the blockchain. Both
parties do not broadcast the Commitment Transactions onto the blockchain until
they want to close out the current balance in the channel. They do so by
broadcasting the present Commitment Transaction.

@@

Since any signed Commitment Transaction may be broadcast on the blockchain, and
only one can be successfully broadcast, it is necessary to prevent old
Commitment Transactions from being broadcast. It is not possible to revoke tens
of thousands of transactions in Bitcoin, so an alternate method is necessary.
Instead of active revocation enforced by the blockchain, it's necessary to
construct the channel itself in similar manner to a Fidelity Bond, whereby both
parties make commitments, and violations of these commitments are enforced by
penalties. If one party violates their agreement, then they will lose all the
money in the channel.

@@

Mark Freidenbach has proposed that Sequence Numbers can be enforcible via a
relative block maturity of the parent transaction via a
soft-fork\cite{seqnum}. This would allow some basic ability to ensure some form
of relative block confirmation time lock on the spending script. In addition, an
additional opcode, OP\_CHECKSEQUENCEVERIFY\cite{csv} (a.k.a.
OP\_RELATIVECHECKLOCKTIMEVERIFY)\cite{relCLTV}, would permit further abilities,
including allowing a stop-gap solution before a more permanent solution for
resolving transaction malleability. A future version of this paper will include
proposed solutions.

@@

However, this requires some kind of flag in the block to designate whether it
is a timestop block. For full SPV compatibility (Simple Payment Verification;
lightweight clients), it is desirable for this to be within the 80-byte block
header instead of in the coinbase. There are two places which may be a good
place to put in this flag in the block header: in the block time and in the
block version. The block time may not be safe due to the last bits being used as
an entropy source for some ASIC miners, therefore a bit may need to be consumed
for timestop flags. Another option would be to hardcode timestop activation as a
hard consensus rule (e.g. via block size), however this may make things less
flexible. By setting sane defaults for timestop rules, these rules can be
changed without consensus soft-forks.

@@

The intent of creating a new Commitment Transaction is to invalidate all old
Commitment Transactions when updating the new balance with a new Commitment
Transaction. Invalidation of old transactions can happen by making an output be
a Revocable Sequence Maturity Contract (RSMC). To invalidate a transaction, a
superseding transaction will be signed and exchanged by both parties that gives
all funds to the counterparty in the event an older transaction is incorrectly
broadcast. The incorrect broadcast is identified by creating two different
Commitment Transactions with the same final balance outputs, however the payment
to oneself is encumbered by an RSMC.

In effect, there are two Commitment Transactions from a single Funding
Transaction 2-of-2 outputs. Of these two Commitment Transactions, only one can
enter into the blockchain. Each party within a channel has one version of this
contract. So if this is the first Commitment Transaction pair, Alice's
Commitment Transaction is defined as C1a, and Bob's Commitment Transaction is
defined as C1b. By broadcasting a Commitment Transaction, one is requesting for
the channel to close out and end. The first two outputs for the Commitment
Transaction include a Delivery Transaction (payout) of the present unallocated
balance to the channel counterparties. If Alice broadcasts C1a, one of the
output is spendable by D1a, which sends funds to Bob. For Bob, C1b is spendable
by D1b, which sends funds to Alice. The Delivery Transaction (D1a/D1b) is
immediately redeemable and is not encumbered in any way in the event the
Commitment Transaction is broadcast.

@@

After the Commitment Transaction has been in the blockchain for 1000 blocks,
Bob can then broadcast the Revocable Delivery transaction. He must wait 1000
blocks to prove he has not revoked this Commitment Transaction (C1b). After
1000 blocks, the Revocable Delivery transaction will be able to be included in a
block. If a party attempt to include the Revocable Delivery transaction in a
block before 1000 confirmations, the transaction will be invalid up until after
1000 confirmations have passed (at which point it will become valid if the
output has not yet been redeemed).

@@

\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1.3\linewidth]{figures/newcommit-br.pdf}
	}
	\caption{
		When C2a and C2b exist, both parties exchange Breach Remedy
		transactions. Both parties now have explicit economic incentive
		to avoid broadcasting old Commitment Transactions (C1a/C1b).
		If either party wishes to close out the channel, they will only
		use C2a (Alice) or C2b (Bob). If Alice broadcasts C1a, all her
		money will go to Bob. If Bob broadcasts C1b, all his money will
		go to Alice. See previous figure for C2a/C2b outputs.
	}
\end{figure}

@@

To create revocable Commitment Transactions, it requires proper construction of
the channel from the beginning, and only signing transactions which may be
broadcast at any time in the future, while ensuring that one will not lose out
due to uncooperative or malicious counterparties. This requires determining
which public key to use for new commitments, as using SIGHASH\_NOINPUT requires
using unique keys for each Commitment Transaction RSMC (and HTLC) output. We use
$P$ to designate pubkeys and $K$ to designate the corresponding private key used
to sign.

When generating the first Commitment Transaction, Alice and Bob agree to create
a multisig output from a Funding Transaction with a single $multisig(P_{AliceF},
P_{BobF})$ output, funded with 0.5 BTC from Alice and Bob for a total of 1 BTC.
This output is a Pay to Script Hash\cite{p2sh} transaction, which requires both
Alice and Bob to both agree to spend from the Funding Transaction. They do not
yet make the Funding Transaction (F) spendable. Additionally, $P_{AliceF}$ and
$P_{BobF}$ are only used for the Funding Transaction, they are not used for
anything else.

Since the Delivery transaction is just a P2PKH output (bitcoin addresses
beginning with 1) or P2SH transaction (commonly recognized as addresses
beginning with the 3) which the counterparties designate beforehand, this can be
generated as an output of $P_{AliceD}$ and $P_{BobD}$. For simplicity, these
output addresses will remain the same throughout the channel, since its funds
are fully controlled by its designated recipient after the Commitment
Transaction enters the blockchain. If desired, but not necessary, both parties
may update and change $P_{AliceD}$ and $P_{BobD}$ for future Commitment
Transactions.

@@

The purpose of an HTLC is to allow for global state across multiple nodes via
hashes. This global state is ensured by time commitments and time-based
unencumbering of resources via disclosure of preimages. Transactional
``locking'' occurs globally via commitments, at any point in time a single
participant is responsible for disclosing to the next participant whether they
have knowledge of the preimage $R$. This construction does not require custodial
trust in one's channel counterparty, nor any other participant in the network.

@@

\begin{figure}[H]
	\makebox[\linewidth]{
		\includegraphics[width=1\linewidth]{figures/htlc-concept.pdf}
	}
	\caption{This is a non-functional naive implementation of an HTLC. Only
		the HTLC path from the Commitment Transaction is displayed. Note
		that there are two possible spends from an HTLC output. If Bob
		can produce the preimage $R$ within 3 days and he can redeem
		path 1. After three days, Alice is able to broadcast path 2.
		When 3 days have elapsed either is valid. This model, however,
		doesn't work with multiple Commitment Transactions.
	}
\end{figure}

@@

After HT1a enters into the blockchain and 1000 block confirmations occur, an
HTLC Timeout Revocable Delivery transaction (HTRD1a) may be broadcast by Alice
which consumes $multisig(P_{Alice3}, P_{Bob3})$. Only Alice can broadcast HTRD1a
1000 blocks after HT1a is broadcast since only Bob gave his signature for HTRD1a
to Alice. This transaction can be revocable when another transaction supersedes
HTRD1a using $multisig(P_{Alice4}, P_{Bob4})$ which does not have any block
maturity requirements.

@@

After HE1b enters into the blockchain and 1000 block confirmations occur, an
HTLC Execution Revocable Delivery transaction (HERD1b) may be broadcast by Bob
which consumes $multisig(P_{Alice7}, P_{Bob7})$. Only Bob can broadcast HERD1b
1000 blocks after HE1b is broadcast since only Alice gave her signature for
HERD1b to Bob. This transaction can be revocable when another transaction
supersedes HERD1b using $multisig(P_{Alice8}, P_{Bob8})$ which does not have any
block maturity requirements.

@@

For example, Alice wishes to terminate the HTLC, Alice will disclose
$K_{Alice1}$ and $K_{Alice4}$ to Bob. Correspondingly if Bob wishes to terminate
the HTLC, Bob will disclose $K_{Bob6}$ and $K_{Bob8}$ to Alice. After the
private keys are disclosed to the counterparty, if Alice broadcasts C2a, Bob
will be able to take all the funds from the HTLC immediately. If Bob broadcasts
C2b, Alice will be able to take all funds from the HTLC immediately. Note that
when an HTLC is terminated, the older Commitment Transaction must be revoked as
well.

@@

Since both parties are able to prove the current state to each other, they can
come to agreement on the current balance inside the channel. Since they may
broadcast the current state on the blockchain, they are able to come to
agreement on netting out and terminating the HTLC with a new Commitment
Transaction.

@@

\begin{enumerate}
	\item Alice signs and sends her signature for RD3b and C3b. At this
		point Bob can elect to broadcast C3b or C2b (with the HTLC) with
		the same payout. Bob is willing after receiving C3b to close out
		C2b.
	\item Bob signs and sends his signature for RD3a and C3a, as well as his
		private keys used for Commitment 2 and the HTLC being
		terminated; he sends Alice $K_{BobRSMC2}$, $K_{Bob5}$, and
		$K_{Bob8}$. At this point Bob should only broadcast C3b and
		should not broadcast C2b as he will lose all his money if he
		does so. Bob has fully revoked C2b and the HTLC. Alice is
		willing after receiving C3a to close out C2b.
	\item Alice signs and sends her signature for RD3b and C3b, as well as
		her private keys used for Commitment 2 and the HTLC being
		terminated; she sends Bob $K_{AliceRSMC2}$, $K_{Bob1}$, and
		$K_{Bob4}$. At this point neither party should broadcast
		Commitment 2, if they do so, their funds will be going to the
		counterparty. The old Commitment and old HTLC are now revoked
		and fully terminated. Only the new Commitment 3 remains, which
		does not have an HTLC.
\end{enumerate}

@@

It is possible for each participant to generate different versions of
transactions to ascribe blame as to who broadcast the transaction on the
blockchain. By having knowledge of who broadcast a transaction and the ability
to ascribe blame, a third party service can be used to hold fees in a 2-of-3
multisig escrow. If one wishes to broadcast the transaction chain instead of
agreeing to do a Funding Close or replacement with a new Commitment Transaction,
one would communicate with the third party and broadcast the chain to the
blockchain. If the counterparty refuses the notice from the third party to
cooperate, the penalty is rewarded to the non-cooperative party. In most
instances, participants may be indifferent to the transaction fees in the event
of an uncooperative counterparty.

@@

It is possible construct a cryptographically provable ``Delivery Versus
Payment'' contract, or pay-to-contract\cite{paytocontract}, as proof of
payment. This proof can be established as knowledge of the input R from hash(R)
as payment of a certain value. By embedding a clause into the contract between
the buyer and seller stating that knowing R is proof of funds sent, the
recipient of funds has no incentive to disclose R unless they have certainty
that they will receive payment. When the funds eventually get pulled from the
buyer by their counterparty in their micropayment channel, R is disclosed as
part of that pull of funds. One can design paper legal documents that specify
that knowledge or disclosure of R implies fulfillment of payment. The sender can
then arrange a cryptographically signed contract with knowledge of inputs for
hashes treated as fulfillment of the paper contract before payment occurs.

@@

The obligation to deliver funds to an end-recipient is achieved through a
process of chained delegation. Each participant along the path assumes the
obligation to deliver to a particular recipient. Each participant passes on this
obligation to the next participant in the path. The obligation of each
subsequent participant along the path, defined in their respective HTLCs, has a
shorter time to completion compared to the prior participant. This way each
participant is sure that they will be able to claim funds when the obligation is
sent along the path.

@@

Decrementing timelocks are used so that all parties along the path know that
the disclosure of R will allow the disclosing party to pull funds, since they
will at worst be pulling funds after the date whereby they must receive R. If
Dave does not produce R within 1 day to Carol, then Carol will be able to close
out the HTLC. If Dave broadcasts R after 1 day, then he will not be able to pull
funds from Carol. Carol's responsibility to Bob occurs on day 2, so Carol will
never be responsible for payment to Dave without an ability to pull funds from
Bob provided that she updates her transaction with Dave via transmission to the
blockchain or via novation.

In the event that R gets disclosed to the participants halfway through expiry
along the path (e.g. day 2), then it is possible for some parties along the
path to be enriched. The sender will be able to know R, so due to Pay to
Contract, the payment will have been fulfilled even though the receiver did not
receive the funds. Therefore, the receiver must never disclose R unless they
have received an HTLC from their channel counterparty; they are guaranteed to
receive payment from one of their channel counterparties upon disclosure of the
preimage.

@@

It is preferable to use a small payment per HTLC. One should not use an
extremely high payment, in case the payment does not fully route to its
destination. If the payment does not reach its destination and one of the
participants along the path is uncooperative, it is possible that the sender
must wait until the expiry before receiving a refund. Delivery may be lossy,
similar to packets on the internet, but the network cannot outright steal funds
in transit. Since transactions don't hit the blockchain with cooperative channel
counterparties, it is recommended to use as small of a payment as possible. A
tradeoff exists between locking up transaction fees on each hop versus the
desire to use as small a transaction amount as possible (the latter of which may
incur higher total fees). Smaller transfers with more intermediaries imply a
higher percentage paid as Lightning Network fees to the intermediaries.

@@

%bibliography
\bibliographystyle{unsrt}
\bibliography{paper}
